%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.2 (25/3/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,letterpaper,sans]{moderncv} 
% Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, 
% executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} 
% CV theme - options include: 'casual' (default), 'classic', 
% 'oldstyle' and 'banking'
\moderncvcolor{blue} 
% CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 
% 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust 
% the width of the space allocated to your name

\setlength\parindent{0pt}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}} 
% Filis Var: To indent a single paragraph

%\usepackage[]{hyperref}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Felipe L.} % Your first name
\familyname{G\'omez-Cort\'es} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Calle 23C 70-50 Int 21 Apt 403}{Bogot\'a, Colombia.}
\mobile{(+57) 316 845 5161}
%\phone{(+571) 759 5221}
%\fax{(000) 111 1113}
\email{flgomezc87@gmail.com}
\homepage{github.com/flgomezc}{https://github.com/flgomezc} 
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, 
% the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------
%
% To remove the cover letter, comment out this entire block
%
%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} 
            % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title


%----------------------------------------------------------------------------------------
%	PROFILE SECTION
%----------------------------------------------------------------------------------------

\section{Profile}

I am Physicist. My research area is Computational Astrophysics. I have developed different 
strong skills in order to solve physical problems; Mathematical Modeling, Data Analysis, 
Python and C++ programming under UNIX-like operating systems. 
\par
\forceindent I am co-founder of a technology company. As entrepreneur I have learned the
Lean Startup methodology, also I have got software developing skills as in back-end as 
well in front-end. I have worked in a couple projects involving Java (Android), MySQL, 
PHP, NodeJS and JavaScript (Facebook Messenger Chatbots).
\par
\forceindent I have teaching at university level as Professor Auxiliar and Graduate Student 
Assistant, I have taught Computational Methods for physicists, first and second year 
(theoretical and experimental) physics courses for natural sciences, health sciences and 
engineering.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cventry{2017}{Co-founder and Chief of Technology Officer}{\textsc{Montanoa Tech S.A.}}
{Bogot\'a, Colombia}{}
{
As CTO, I have been Back-end and Front-end Head Developer. I have learned Java for Android
mobile apps, some basics of Apache2 running on Ubuntu Server 14.10. 
We have participated in the Apps.CO/MINTIC official contest 
``Convocatoria a Equipos de Emprendedores para la Fase de Descubrimiento de
Negocios TIC de la Iniciativa APPS.CO'' with the project ``Pedro App''.
The purpose of this contest is to give teaching and accompaniment for new entrepreneur 
teams.
We have learned the Lean Startup methodology. Our MVP is a delivery system joint with a 
Facebook Chatbot to order freshly baked goods on demand. \\
Ministerio de Tecnolog\'ias de la informaci\'on y las Comunicaciones (MINTIC).
}

\cventry{2016-II}{Professor Auxiliar}{\textsc{Universidad Manuela Beltr\'an}}
{Bogot\'a, Colombia}{}
{Full time auxiliar professor. I was teaching for health sciences and engineering 
students experimental physics courses for first and second year.}

\cventry{2015-II}{Graduate Teaching Assistant}{\textsc{Universidad de Los Andes}}
{Bogot\'a, Colombia}{}
{Assistant Lecturer of \textbf{Herramientas Computacionales (Computation Tools)} for 
Physics and  Science. This course requires object-oriented programming knowledge. 
\\Dedication: 8 hours per week.
\newline
\href{https://github.com/ComputoCienciasUniandes/HerramientasComputacionales/tree/master/Lectures/98.Python}
{\textcolor{blue}{Website, videos, resources and exercises.}}
\newline{}
Syllabus:
\begin{itemize}
\item UNIX systems basics.
\item Introducing the Python programming language.
\item Algorithms
\item Numerical Methods (derivation, integration, differential equations)
\item Solving Physical Systems
\end{itemize}}

\cventry{2015-II}{Graduate Teaching Assistant}
{\textsc{Universidad de Los Andes}}{Bogot\'a, Colombia}{}
{Graduate Teaching Assistant of \textbf{M\'etodos Computacionales (Computation Methods)} 
for Physics and Science using Python and C. In this course Advanced numerical methods 
are taugth, like Runge-Kutta in coupled differential equations, finite differences and
 Monte Carlo applications.\\
Dedication: 4 hours per week.}

%------------------------------------------------

\cventry{2013-II 2014-II}{Graduate Teaching Assistant}
{\textsc{Universidad de Los Andes}}
{Bogot\'a, Colombia}{}
{Graduate Teaching Assistant of \textbf{Experimental Physics I \& II} and 
\textbf{Physics II (Complementary Section)} for Science and Engineering.}

%------------------------------------------------

\cventry{2013-I}{Academic Teacher}
{\textsc{Batakl\'an Corporaci\'on de Artes}}
{Bogot\'a, Colombia}{}
{Teacher of \textbf{Art and Science} for elementary and high school.}

\cventry{2013-I}{Academic Teacher}
{\textsc{Fundaci\'on San Jos\'e}}
{Bogot\'a, Colombia}{}
{Teacher of \textbf{Mathematics and Statistics} for Business Management and Engineering.}

%------------------------------------------------

\cventry{2009--2010}
{Astronomy Auxiliar Student}
{\textsc{Universidad Nacional de Colombia}}
{Bogot\'a, Colombia.}{}
{Course ``Astronom\'ia Para Todos'' (Astronomy for Everybody) at Observatorio 
Astron\'omico Nacional.}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

Please check some projects in my repo at \url{https://github.com/flgomezc}
\medskip

\begin{itemize}
\item Java (Android) \url{https://github.com/flgomezc/movies-app}
\item Facebook Bot (Node-JavaScript) \url{https://github.com/flgomezc/pedrobot}
\item Python, Ipython Notebook, \LaTeX \url{https://github.com/flgomezc/sfr-dmhm}
\end{itemize}

\medskip

\cvitem{Basic}{R, PHP, Apache2}
\cvitem{Intermediate}{\textsc{C++}, Java, MySQL, GIT and Unix-like OS.}
\cvitem{Advanced}{\textsc{Python} with the IPython Notebook (Jupyter), Matplotlib and 
Numpy modules. \LaTeX, \textsc{JavaScript} and Asynchronous programming with the
Facebook API for Messenger Chatbots}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2014--2015}
{PhD. Physics (Retired)}
{Universidad de Los Andes}
{Bogot\'a, Colombia}{}{
My research field is Computational Astrophysics, dark matter and galaxy formation in 
early universe. I was internship student at the Purdue University (Indiana, USA) by one 
semester (2015-I).
I attended the Dark Energy Spectroscopic Instrument (DESI) International Collaboration May 
2015 Meeting at the FERMILAB (Illinois, USA). 
Also I have assisted to the workshop nIFTy Cosmology: Numerical Simulations for Large 
Surveys hosted by Universidad Aut\'onoma de Madrid, (Madrid, Espa\~na, 2014-summer). 
I was retired from the PhD. program due to health issues.}

\cventry{2013--2014}
{M.Sc. Physics (Postponed)}
{Universidad de Los Andes}
{Bogot\'a, Colombia}{}{I started here my formation in Computational Astrophysics. After
one year I decided to move to the PhD. program, postponing the Master's degree.}  

\cventry{2013}{B.Sc. Physics}{Universidad Nacional de Colombia}{Bogot\'a, Colombia}{}{
As undergrad student I have explored computational and experimental physics areas. My
degree thesis was on experimental physics, measuring ion beam currents in a low energy
particle accelerator.
}

\bigskip

\subsection{Masters Thesis (In Progress)}
\cvitem{Title}{\emph{A Connection Between Star Formation Rate and Dark Matter Halos at 
z$\sim$6}.}
\cvitem{Adviser}{Professor Jaime Forero-Romero}
\cvitem{Description}{This work relates ordinary matter and dark matter in the early 
Universe using telescope observations and halo catalogs from simulations using
a Markov-Chain MoteCarlo method.}
\cvitem{Keywords}{Large Scale Structure, Galaxy Evolution, Computational Astrophysics.}

\medskip

\subsection{Bachelor Thesis}
\cvitem{Title}{Mass Characterization of the $H_3 ^+$ and $H ^-$ Ion Beam From a Plasmatron
Ion Source. 2012}
\cvitem{Director}{Professor Gustavo Mart\'inez Tamayo}
\cvitem{Description}{This work studied how the change of the geometry of the thermionic 
emission filament in the UNAC-Plasmatron (ion source) generates a change in the ion 
production and the ion beam.}
\cvitem{Keywords}{Plasma, Ion Beam, $H ^-$ Ion, Experimental Physics.}

\medskip

\subsection{Other}

\cvitem{January 2016}{\textbf{PADI Scuba Diver}, Reef Shepherd Professional Dive Center, 
Santa Marta, Colombia. }

\cvitem{2015-I}{Internship at \textbf{Purdue University, Indiana, USA}.  Colciencias 
scholarship holder.}

\cvitem{July 2014}{\textbf{nIFTy Cosmology: Numerical Simulations for Large Surveys} 
Universidad Aut\'onoma de Madrid, Madrid, Espa\~na.
\newline
\url{http://popia.ft.uam.es/nIFTyCosmology/Home.html}}

\cvitem{January 2014}{\textbf{Cosmology on the Beach: Essential Cosmology for the 
Next Generation.} Berkeley Center for Cosmological Physics and Advanced Institute for 
Cosmology (M\'exico). Cabo San Lucas, M\'exico.
\newline
\url{http://bccp.berkeley.edu/beach_program/index2014.html}
}

\cvitem{June 2013}{\textbf{Workshop Astronom\'ia en Los Andes}, Uniandes, Bogot\'a, 
Colombia}

\cvitem{2012}{\textbf{Circuits and Electronics 6.002x.} Online course of the MIT.
\newline
\url{http://6002x.mitx.mit.edu/info}}

\cvitem{October 2010}{\textbf{Workshop on Physics and Technology at CERN}, UNAL, 
Bogot\'a, Colombia}
\cvitem{August-2010}{\textbf{Escuela de Astronom\'ia Extragal\'actica} Observatorio 
Astron\'omico Nacional, Bogot\'a , Colombia.}

\cvitem{October 2009}{\textbf{XXIII Congreso Nacional de F\'isica, Universidad del 
Magdalena}, Santa Marta, Colombia.
\newline
\url{www.sociedadcolombianadefisica.org.co/pag/eventos2009.php}}

\cvitem{2008}{\textbf{Short Tale Workshop``Ciudad de Bogot\'a 2008.''} Fellow of the
Capital District in the workshop adjoint to RENATA (Red Nacional de Talleres de 
Escritura Creativa)}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Awards}
\cvitem{2011-II}{Mejor Saber-Pro 2011-2 en F\'isica. ICFES.
\newline
\href{http://www.icfes.gov.co/index.php/instituciones-educativas/saber-pro/mejores-saber-pro}
{Top National Physics Bachelor Student. The list is available at www.icfes.gov.co}
}

%------------------------------------------------

\section{Publications}
\cvitem{2013}{\textbf{Experiments with Polygonal and Polyhedral Resistive Structures.}
\textit{R. Beltr\'an, F. G\'omez, R Franco, J-Alexis Rodr\'iguez and F. Fajardo,}
Latin American Journal of Physics Education Vol 7, Issue 4, Dec 2013, 621-624
\newline
\url{www.lajpe.org/index_dec2013.html}
}

\cvitem{2010}{\textbf{Cenizas en el And\'en. Antolog\'ia de Cuento Urbano.} 
City Short Tales Antology, story tittle: \textbf{Imag\'inate} as Filipo Rviz. 
ISBN 978-958-44-4585-8. 
\newline
\url{https://es.wikipedia.org/wiki/Cenizas\_en\_el\_and\%C3\%A9n}}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\section{Languages}
\cvitemwithcomment{Spanish}{Native Speaker}{}
\cvitemwithcomment{English}{B2 Level}
{Common European Framework of Reference. BULATS Test. 2011.}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Reading}{Writing}
\cvlistdoubleitem{Swimming}{Diving}
\cvlistdoubleitem{Guitar}{Riding Bike}
%\cvlistitem{Running}

%----------------------------------------------------------------------------------------

\end{document}
