%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.2 (25/3/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name


%\usepackage[]{hyperref}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Felipe L.} % Your first name
\familyname{G\'omez-Cort\'es} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Calle 23C 70-50 Int 21 Apt 403}{Bogot\'a, Colombia.}
\mobile{(+57) 316 845 5161}
\phone{(+571) 759 5221}
%\fax{(000) 111 1113}
\email{flgomezc87@gmail.com}
\homepage{github.com/flgomezc}{https://github.com/flgomezc} 
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------
%
% To remove the cover letter, comment out this entire block
%
%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2013--2014}{M.Sc. Physics}{Universidad de Los Andes}{Bogot\'a, Colombia.}{}{\textit{Postponed}}  % Arguments not required can be left empty
\cventry{2013}{B.Sc. Physics}{Universidad Nacional de Colombia}{Bogot\'a, Colombia.}{}{}

\subsection{Masters Thesis (In Progress)}
\cvitem{Title}{\emph{A Conection Between Star Formation Rate and Dark Matter Halos at z$\sim$6}.}
\cvitem{Supervisor}{Professor Jaime Forero-Romero}
\cvitem{Description}{This work relates ordinary matter and dark matter in the early 
Universe using telescope observations and halo catalogs from simulations using
a MCMC method.}
\cvitem{Keywords}{Large Scale Structure, Galaxy Evolution, Computational Astrophysics.}


\subsection{Bachelor Thesis}
\cvitem{Title}{Mass Characterization of the $H_3 ^+$ and $H ^-$ Ion Beam From a Plasmatron
Ion Source. 2012}
\cvitem{Director}{Professor Gustavo Mart\'inez Tamayo}
\cvitem{Description}{This work studied how the change of the geometry of the thermionic 
emission filament in the UNAC-Plasmatron (ion source) generates a change in the ion 
production and the ion beam.}
\cvitem{Keyords}{Plasma, Ion Beam, $H ^-$ Ion, Experimental Physics.}

\subsection{Other}

\cvitem{2016}{\textbf{The Analytical Edge}, MIT online course. Actyally enrolled.
\newline
\url{https://www.edx.org/course/analytics-edge-mitx-15-071x-2}}

\cvitem{January 2016}{\textbf{PADI Scuba Diver}, Reef Shepherd Professional Dive Center, Santa Marta, Colombia. }

\cvitem{2015-I}{Internship at \textbf{Purdue University, Indiana, USA}.  Colciencias scholarship holder.}

\cvitem{July 2014}{\textbf{nIFTy Cosmology: Numerical Simulations for Large Surveys} Universidad Aut\'onoma de Madrid, Madrid, Espa\~na.
\newline
\url{http://popia.ft.uam.es/nIFTyCosmology/Home.html}}

\cvitem{January 2014}{\textbf{Cosmology on the Beach: Essential Cosmology for the Next Generation.} Berkeley Center for Cosmological Physics and Advanced Institute for Cosmology (M\'exico). Cabo San Lucas, M\'exico.
\newline
\url{http://bccp.berkeley.edu/beach_program/index2014.html}
}

\cvitem{June 2013}{\textbf{Workshop Astronom\'ia en Los Andes}, Uniandes, Bogot\'a, Colombia}

\cvitem{2012}{\textbf{Circuits and Electronics 6.002x.} Online course of the MIT.
\newline
\url{http://6002x.mitx.mit.edu/info}}

\cvitem{October 2010}{\textbf{Workshop on Physics and Thechnology at CERN}, UNAL, Bogot\'a, Colombia}
\cvitem{August-2010}{\textbf{Escuela de Astronom\'ia Extragal\'actica} Observatorio Astron\'omico Nacional, Bogot\'a , Colombia.}

\cvitem{October 2009}{\textbf{XXIII Congreso Nacional de F\'isica, Universidad del Magdalena}, Santa Marta, Colombia.
\newline
\url{www.sociedadcolombianadefisica.org.co/pag/eventos2009.php}}

\cvitem{2008}{\textbf{Short Tale Workshop``Ciudad de Bogot\'a 2008.''} Fellow of the
Capital District in the workshop adjoint to RENATA (Red Nacional de Talleres de 
Escritura Creativa)}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Vocational}

\cventry{2015-2}{Graduate Assistant}{\textsc{Universidad de Los Andes}}{Bogot\'a, Colombia}{}
{Teacher of \textbf{Herramientas Computacionales (Computation Tools)} for Physics and Science. 
Dedication: 8 hours per week.
\newline
\href{https://github.com/ComputoCienciasUniandes/HerramientasComputacionales/tree/master/Lectures/98.Python}
{\textcolor{blue}{Website, videos, resources and excercises.}}
\newline{}
Syllabus:
\begin{itemize}
\item Basics of UNIX systems.
\item Introducing the Python programming language.
\item Algorythms
\item Solving Physical Systems
\end{itemize}}

\cventry{2015-2}{Graduate Assistant}{\textsc{Universidad de Los Andes}}{Bogot\'a, Colombia}{}
{Teacher Assistant of \textbf{M\'etodos Computacionales (Computation Methods)} for Physics and Science
using Python and C. Dedication: 4 hours per week.}

%------------------------------------------------

\cventry{2013-II 2014-II}{Graduate Assistant}{\textsc{Universidad de Los Andes}}{Bogot\'a, Colombia}{}
{Teacher of \textbf{Experimental Physics I \& II} and \textbf{Physics II (Complementary Section)} 
for Science and Engineering.}

%------------------------------------------------

\cventry{2013-I}{Academic Teacher}{\textsc{Batakl\'an Corporaci\'on de Artes}}{Bogot\'a, Colombia}{}
{Teacher of \textbf{Art and Science} for elemmentary and high school.}

\cventry{2013-I}{Academic Teacher}{\textsc{Fundaci\'on San Jos\'e}}{Bogot\'a, Colombia}{}
{Teacher of \textbf{Mathemathics and Statistics} for Bussiness Managment and Engineering.}

%------------------------------------------------
\subsection{Miscellaneous}

\cventry{2009--2010}{Astronomy Auxiliar Student}{\textsc{Universidad Nacional de Colombia}}{Bogot\'a, Colombia.}{}
{Course ``Astronom\'ia Para Todos'' (Astronomy for Everybody) at the National Obervatory.}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Awards}
\cvitem{2011-II}{Mejor Saber-Pro 2011-2 en F\'isica. ICFES.
\newline
\href{http://www.icfes.gov.co/index.php/instituciones-educativas/saber-pro/mejores-saber-pro}{Top National Physics Bachelor Student. The list is available at www.icfes.gov.co}
}

%------------------------------------------------

\section{Publications}
\cvitem{2013}{\textbf{Experiments with Polygonal and Polyhedral Resistive Structures.}
\textit{R. Beltr\'an, F. G\'omez, R Franco, J-Alexis Rodr\'iguez and F. Fajardo,}
Latin American Journal of Physics Education Vol 7, Issue 4, Dec 2013, 621-624
\newline
\url{www.lajpe.org/index_dec2013.html}
}

\cvitem{2010}{\textbf{Cenizas en el And\'en. Antolog\'ia de Cuento Urbano.} 
City Short Tales Antology, story tittle: \textbf{Imag\'inate} as Filipo Rviz. ISBN 978-958-44-4585-8. 
\newline
\url{https://es.wikipedia.org/wiki/Cenizas\_en\_el\_and\%C3\%A9n}}



%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{R}}
\cvitem{Intermediate}{\textsc{C++}, \textsc{Java}, \LaTeX, OpenOffice, Linux, Microsoft Windows}
\cvitem{Advanced}{\textsc{Python}}



%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\section{Languages}
\cvitemwithcomment{Spanish}{Native Speaker}{}
\cvitemwithcomment{English}{B2 Level}{Common European Framework of Reference. BULATS Test. 2011.}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Reading}{Writting}
\cvlistdoubleitem{Swimming}{Diving}
\cvlistdoubleitem{Guitar}{Riding Bike}
%\cvlistitem{Running}

%----------------------------------------------------------------------------------------

\end{document}
